---
title: "Immunisation Rates Presentation"
author: "Natalie Phillips"
date: "19 August 2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.path = 'figure/')
library(xlsx)
library(dplyr)
library(xlsx)
```

## Immunisation Rates in Australia

There are new laws in Australia limiting financial assistance to families where children are not immunised. It is important we understand the rate of immunisation in this country.

The statistics in this presentation were gathered from the [Immunise Australia Program](http://www.immunise.health.gov.au/) webpage from the Australian Government - Department of Health.

Create the data folders.


```{r creatDataFolder, message=FALSE, warning=FALSE}
#Create a data directory if one doesn't already exist
if (!file.exists("data")){
    dir.create("data")
}
if (!file.exists("data\\base")){
    dir.create("data\\base")
}
if (!file.exists("data\\processed")){
    dir.create("data\\processed")
}
```

Download the data from the website.


```{r download, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
dataDetails <- read.xlsx2(
    file = ".\\data\\dataDetails.xlsx"
    ,sheetName = "Sheet1"
)

readFile <- function(x){
    if(!file.exists(x[2])){
        download.file(
            x[1]
            ,destfile = x[2]
            ,mode = "wb"
        )
    }
}
invisible(apply(dataDetails, 1, readFile))

```

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

