---
title: "Immunisation Rates In Australia"
author: "Natalie Phillips"
date: "19 August 2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.path = 'figure/')
library(xlsx)
library(dplyr)
library(tidyr)
library(zoo)
library(xts)
library(dygraphs)
library(ggplot2)
```

## Immunisation Rates in Australia

It is important we understand the rate of immunisation in Australia. There are new laws in Australia limiting financial assistance to families where children are not immunised. It is also important for planning medical programs and advertising campaigns.

This app provides a simple way to see how different types of immunisations are taken up in the comunity when compared to the total immunisation rates.  You can also see the variance over time in different regions in Australia. The app can be found at <https://nattsapps.shinyapps.io/ImmunisationRates/>

To do this I have leveraged publicly available immunisation data from the government.


## Getting the data

The statistics in this presentation were gathered from the [Immunise Australia Program](http://www.immunise.health.gov.au/) webpage from the Australian Government - Department of Health.


```{r creatDataFolder, message=FALSE, warning=FALSE}
#Create a data directory if one doesn't already exist
if (!file.exists("data")){
    dir.create("data")
}
if (!file.exists("data\\base")){
    dir.create("data\\base")
}
if (!file.exists("data\\processed")){
    dir.create("data\\processed")
}
```

### Obtaining and loading the data

I manually compiled the details of the required files in a file called dataDetails.xlsx. I included URL, SheetName, StartRow etc. Before downloaing all files into a local data folder.


```{r download, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
dataDetails <- read.xlsx2(
    file = ".\\data\\dataDetails.xlsx"
    ,sheetName = "Sheet1"
    ,colClasses = c(
        "character"
        ,"character"
        ,"character"
        ,"numeric"
        ,"numeric"
        ,"numeric"
        ,"character"
    )
)
```

```{r show, echo = TRUE}
readFile <- function(x){
    if(!file.exists(x[2])){
        download.file(
            x[1]
            ,destfile = x[2]
            ,mode = "wb"
        )
    }
}
invisible(apply(dataDetails, 1, readFile))

```

The full data is contained in eight separate spreadsheets. All eight spreadsheets are  read into a single dataframe noting the unique "date of processing" of each file. This data is now ready for use and further refinement in the shiny app.

```{r defineFun, echo=FALSE}
immClasses <- c(
    "character"
    ,"character"
    ,"character"
    ,"numeric"
    ,"numeric"
    ,"numeric"
    ,"numeric"
    ,"numeric"
    ,"numeric"
    ,"numeric"
    ,"numeric"
    ,"numeric"
)

colClean <- function(x){
    colnames(x) <- gsub("\\.+", "_", colnames(x));
    colnames(x) <- gsub("X_", "PCT_", colnames(x));
    colnames(x) <- gsub("_$", "", colnames(x));
    x 
}

ageFactors <- function(x){
    x <- factor(
        x
        ,levels = c(
            "12-<15 Months"
            ,"24-<27 Months"
            ,"60-<63 Months"
        )
        ,ordered=TRUE
    );
    x
}

readFile2 <- function(x){
    immData <- read.xlsx2(
        file = x[[2]]
        ,sheetName = x[[3]]
        ,startRow = as.numeric(x[4])
        ,endRow = as.numeric(x[5])
        ,colClasses = immClasses
    )
    immData <- colClean(immData)

    immData <- mutate(immData, Time_Period = as.Date(as.numeric(x[6])-2, 
                                                     origin="1900-01-01"))
}

```

```{r load,cache=TRUE, echo=TRUE}
allframes <- apply(dataDetails, 1, readFile2)

immDataAll <- do.call(rbind,allframes)

immDataAll$Age_Group <- ageFactors(immDataAll$Age_Group)

save(immDataAll, file = ".\\data\\processed\\immDataAll.Rda")

summary(immDataAll)


```



## Interactive vaccination rates plot

To provide a clear way to view vaccination rates for different types of vaccine I have provide an interactive plot that allows you to choose which vaccine to compare to the rates of fully vaccinated children. This can be useful to show if there is higher risk of particular illness in Australian children.

Depending on which vaccination rate you choose I subset the data and plot the output. A short extract of some server.R commands follows. In the real server.R there is one plotData command for each vaccination type:

```{r interactive, echo=TRUE, eval=FALSE}
load("./data/immDataAll.Rda")
shinyServer(function(input, output) {
    output$distPlot <- renderPlot({
        if (input$vacc=='PCT_DTP'){
            plotData <- immDataAll %>% 
                select(PCT_DTP, PCT_Fully) %>%
                filter(PCT_DTP > 0)
        } else if (input$vacc=="PCT_Polio"){
            plotData <- immDataAll %>% 
                select(PCT_Polio, PCT_Fully) %>%
                filter(PCT_Polio > 0)
        } else if (input$vacc=="PCT_HIB") {
            
        ...

        
        plot(plotData$x,
             plotData$PCT_Fully,
             
             main="Total vaccination rate against individual vaccinations",
             ylab = "Total vaccination rate",
             
             xlab = if (input$vacc=='PCT_DTP'){
                 xlab = "Diphtheria tetanus and pertussis whooping cough"
             } else if (input$vacc=="PCT_Polio"){
                 xlab = "Polio"
                 
            ...
```


## Total vaccination rate - time series plot by region

It is important to be able to see if there is variation in vaccination rates across regions of Australia. This is useful for medical planning and to see if advertising campaigns are effective.

This data needed more manipulation in order to plot the changes over time for the different regions. In order to show more than one time series the data was first made long. Then I subsetted the data to a managable number of datapoints. I choose fully imminised rates for the oldest bracket of children across all regions and times.

```{r timeSeries, echo=TRUE}
immDataLong <- immDataAll %>%
    gather("Vaccination", "Percent", 4:12)

immDataRegion <- immDataLong %>%
    filter(Age_Group == "60-<63 Months") %>%
    mutate(Region_Type = paste(PHN_Name,Vaccination, sep = "_")) %>%
    select(c(Region_Type, Time_Period, Percent)) %>%
    filter(grepl('Fully', Region_Type))

head(immDataRegion)
```

